---
title: 'Ensuring reproducibility'
teaching: 15
exercises: 10
---

::::::::::::::::::::::::::::::::::::::: objectives

- Understand the different concepts related to reproducibility.
- Learn about methods to capture reproducible research environments.
- Understand the concept of provenance and version control.
- Understand the power and pitfalls of Git


::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- How to build reproducible analysis?
- how to deal with dependencies?

- What is version control?
- Why using git ?
- How is version control system relevant for biomedical research?

::::::::::::::::::::::::::::::::::::::::::::::::::




```{r, child='files/04-reproducibility.md'}
```

<br><br><br><br>

---

<br><br>

```{r, child='files/05-versioncontrol.md'}
```

::::::::::::::::::::::::::::::::::::::::::::::: discussion

- Which of the reproducible research principles are you already implementing in your work and how?

- How do you currently version control your projects? What changes will you introduce to ensure fair credit and citation of your and your team's work?

- What are other measures to ensure reproducibility in your research documentation and that of your team?"

::::::::::::::::::::::::::::::::::::::::::::::::::






