---
title: 'Managing project start and collaborations'
teaching: 40
exercises: 10
---

::::::::::::::::::::::::::::::::::::::: objectives

- Describe best practices for setting a project repository
- Build a basis for collaboration and co-creation in team projects
- Plan computational reproducibility and project management practices
- Make it easy for each contributor to participate, contribute and be recognised for their work

- Demonstrate GitHub Project Board to enable project management.
- Discuss the importance of code quality, modular programming, and code testing for reusable error-free code.
- Encourage researchers to combine code with documentation to communicate their work.
- Learn about methods to capture reproducible research environments.
::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- How to set up a computational project?
- What main concerns and challenges exist and how to address them?
- How to create a project repository for sharing, collaboration and an intention to release?
- What extra tools may be used ?

- How to manage and oversee tasks and track progress of your projects?
- How collaborative practices help ensure code quality, testing and reuse?
- What is literate programming and how does it help with early communication, testing and collaboration?

::::::::::::::::::::::::::::::::::::::::::::::::::

```{r, child='files/07-setup.md'}
```

```{r, child='files/08-collaborativeworking.md'}
```
