---
title: 'Managing project start and collaborations'
teaching: 25
exercises: 50
---

::::::::::::::::::::::::::::::::::::::: objectives

- Describe best practices for setting a project repository
- Build a basis for collaboration and co-creation in team projects
- Plan computational reproducibility and project management practices
- Make it easy for each contributor to participate, contribute and be recognised for their work

- Demonstrate GitHub Project Board to enable project management.
::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- How to set up a computational project?
- What main concerns and challenges exist and how to address them?
- How to create a project repository for sharing, collaboration and an intention to release?
- What extra tools may be used ?

- How to manage and oversee tasks and track progress of your projects?
- How collaborative practices help ensure code quality, testing and reuse?
- What is literate programming and how does it help with early communication, testing and collaboration?

::::::::::::::::::::::::::::::::::::::::::::::::::

```{r, child='files/07-setup.md'}
```

<br><br><br><br>

---

<br><br>

```{r, child='files/08-collaborativeworking.md'}
```

:::: discussion

What measures described in this session are meant to make research more reproducible, what measures are meant to facilitate team work. How does the different measures interact ?

::::: spoiler

### Authors' summary

Making interaction measure is also making the research more reproducible. Indeed most of the reusability of the data and code can be best tested when several people interact on a project. Documenting for a current collaborator helps a lot to make sure documentation will be enough for new collaboratory coming in the project later on.
:::::

::::
