---
title: 'Managing code'
teaching: 40
exercises: 10
---

::::::::::::::::::::::::::::::::::::::: objectives

- Understand the basics of coding 
- Understand the advantages of modular code
- How to foster good practices:
  - using code review
  - using tests
- Discuss the importance of code quality, modular programming, and code testing for reusable error-free code.
- Encourage researchers to combine code with documentation to communicate their work.

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- What is the role of data wrangling?
- What is literate programming?
- How to use data visualisation for insight and communication?

- What are the main objectives and best practices for testing and reviewing code?
- When can continuous integration help?


::::::::::::::::::::::::::::::::::::::::::::::::::

## Basics of coding

As a project manager, you do not need to code or know how coding works.
However, it is important to understand the data workflow and foster documentation, as well as coding best practices, such that you can understand the analysis. 

This chapter gives a small introduction into coding and data analysis workflow, code modularity, and then how foster good code with tests and review.

```{r, child='files/12-analysis.md'}
```

```{r, child='files/14-codemodularity.md'}
```

```{r, child='files/13-codereview.md'}
```


