---
title: 'Managing code'
teaching: 40
exercises: 10
---

::::::::::::::::::::::::::::::::::::::: objectives

- First learning objective. (FIXME)
- To make informed decisions using data.

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- What is the role of data wrangling?
- What is literate programming?
- How to use data visualisation for insight and communication?

::::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::: objectives

- Explain different processes and best practices for code review.
- Discuss tips, tricks and benefits of code review.
- Share some ways to involve all group members in code review.

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- What are the main objectives and best practices for testing and reviewing code?
- What can continous integration help?
- How can group leaders facilitate a collaborative environment for code review?

::::::::::::::::::::::::::::::::::::::::::::::::::

```{r, child='files/12-analysis.md'}
```

```{r, child='files/13-codereview.md'}
```

```{r, child='files/14-codemodularity.md'}
```
