---
title: 'Managing publication'
teaching: 40
exercises: 10
---

::::::::::::::::::::::::::::::::::::::: objectives

- Understand the importance of PID.
- Know how to make data and code citable
- Share open science practices for transparent and ethical research
- Nudge the use of GitHub/GitLab for open collaboration
- Learn why and how to cite the work of others, as well as your own research output

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- Why should I make my research objects available?
- What open source tools to use for applying data science practices in bioscience?
- How to get your research work cited and invite more contributions to your project?
- How to maintain history of contributions and contributors?
- How should I mention and cite the software or data I am using
::::::::::::::::::::::::::::::::::::::::::::::::::





```{r, child='files/15-publication.md'}
```

```{r, child='files/16-open.md'}
```

```{r, child='files/17-citation.md'}
```
